---
title: "P8105 HW1"
author: "Hansheng Zhang"
date: 2021-09-28
output: github_document
---

# Problem 1

A random sample of size 10 from a standard Normal distribution

```{r}
library(tidyverse)

hw1_df = tibble(
  samp = rnorm(10),
  vec_logical = ifelse(samp > 0, TRUE, FALSE),
  vec_char = rep(c("New York", "Chicago", "Los Angeles"), length.out = 10),
  vec_factor = factor(rep(c("East Coast", "Midwest", "West Coast"), length.out = 10))
)

hw1_df

mean(hw1_df$samp)
mean(hw1_df$vec_logical)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)
```

It appears we can take the mean of the random numbers and the logical vector but not the character vector or the factor vector.

```{r, eval = FALSE}
as.numeric(hw1_df$samp)
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_char)
as.numeric(hw1_df$vec_factor)
```

The random numbers and logical vector are actually numbers. The character vector appears as NA since it is a string, and factor vector translates to levels, but not numbers. Therefore, the mean can only be taken for the first two. 

# Problem 2

## Palmer Penguins
```{r}
data("penguins", package = "palmerpenguins")

rows = nrow(penguins)
cols = ncol(penguins)
total = rows*cols

penguin_variables = names(penguins)

mean_flipper = penguins %>% drop_na() %>% summarise(mean(flipper_length_mm)) %>% round(digits = 2)
```

There are **`r rows`** rows and **`r cols`** columns in this data set for a total of **`r total`** values.

The variables in this data set are **`r penguin_variables`**

The mean flipper length is **`r mean_flipper`** mm.

```{r}
scatter = penguins %>% drop_na() %>% 
ggplot((aes(bill_length_mm, flipper_length_mm, color = species))) + geom_point()

ggsave("hw1_scatterplot.pdf", plot = scatter)

scatter
```